%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%IMPORTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{article}

\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{fontspec}
\usepackage[hidelinks]{hyperref}
\usepackage[dvipsnames]{xcolor}
\setmainfont[Ligatures=TeX]{Verdana}

\begin{document}
\begin{center}
\pagenumbering{gobble}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%HEADINGS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\LARGE Shritesh Jamulkar \\

\vspace{3pt}

\large \textcolor{NavyBlue}{\href{mailto:shritesh.sj@gmail@gmail.com}{shritesh.sj@gmail.com} || \href{tel:+447405656340}{+44 740 5656302} || Skilled Worker Visa} \\

\vspace{3pt}

\normalsize \href{https://linkedin.com/in/shritesh99}{linkedin.com/in/shritesh99} || \href{https://github.com/Shritesh99}{github.com/Shritesh99} || \href{https://leetcode.com/rxshri99}{leetcode.com/rxshri99} \\
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%WORK-EXPERIENCE%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \large \textbf{\textcolor{NavyBlue}{Work Experience}} \vspace{3pt} \\
\noindent \normalsize \textbf{THG - The Hut Group} \hfill Manchester, UK \\
\textit{Software Engineer} \hfill 11/2023 - Present
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item {\normalsize {Stockmanager and various other microservices - In Stock and Availability Team }
        \begin{itemize}
            \item Worked extensively with Spring and Angular frameworks to deliver scalable front-end and back-end solutions, including developing user-friendly UIs and robust services with over 90\% unit test coverage.
            \item Moved legacy Tomcat-based servers to a Kubernetes-based architecture and designed Jenkins pipelines for a seamless deployment process, reducing manual jar deployments. This improved deployment time from 30 minutes to 10 minutes using Docker-based containerized deployment.
            \item Worked with Microsoft SQL Server, CockroachDB, and CouchDB (SQL \& NoSQL). Reduced database overheads by migrating legacy queries to batched queries, significantly decreasing application crashes and reducing query wait times by 40\%. Efficiently provided data to stakeholders by writing and debugging SQL \& NoSQL queries, supporting daily operations and troubleshooting issues across multiple teams.
            \item Led 3+ key client integrations for warehouse management, resolving stock discrepancies and providing hypercare support for resolving complex issues, while ensuring on-time delivery and smooth collaboration across various teams.
            \item Showcased advanced debugging skills for various clients, stakeholders, and marketing teams by independently resolving 90\% of complex issues in legacy systems, significantly reducing the need for senior team intervention.
            \item Implemented monitoring and alerting systems to track infrastructure health and application performance, improving uptime by 20\% and ensuring swift issue resolution during production incidents.
        \end{itemize}
    }
\end{itemize}
\noindent \normalsize \textbf{Samsung Research \& Development Institute, Banglore} \hfill Banglore, India \\
\textit{Software Engineer} \hfill 07/2021 - Present
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item {\normalsize {LTE System Manager (LSM) Project - In Management Software \& Analytics Team }
        \begin{itemize}
            \item Functioning in Telecom Domain as part of Network Management System in Element Management System (EMS), which handles one or more telecommunications network elements.
            \item Engineered a backend Golang-based LSM project, specializing in FM (Fault microservice); executed agile development practices and delivered the project on time and under budget.
            \item Designed and implemented gRPC-based communication between microservices, enabling efficient and language-agnostic communication.
            \item Worked on asynchronous processing using tools like Apache Kafka to handle background tasks and event-driven architecture.
            \item Collaborated on the React-based frontend application feature development for the Fault Module UI.
            \item Optimized performance by lazy loading components and implementing code-splitting to reduce initial load times.
            \item Set up and maintained state management solutions like Redux or Context API to manage application-wide state and data sharing between components.
            \item Implemented comprehensive testing strategies, including unit tests, integration tests, and end-to-end tests, to ensure the reliability and robustness of microservices.
            \item Contributed to Python selenium-based automation testing for the entire Element Management System (EMS) software.
            \item Providing TAC3 support to 4G networks efficiently for JIO, SKT, KT, UQ, KDDI, LGT, KPS, and others.
        \end{itemize}
    }
    \item {\normalsize {Research and Patents Works}
        \begin{itemize}
            \item Collaborated with the blockchain team in various research projects in the blockchain space.
            \item Enlightened team on advanced topics like ZK-SNKRKs, ZK-STARKs, Bulletproofs, etc. and designed various documents on the same.
        \end{itemize}
    }
    \item {\normalsize {Samsung Software Competency Test (SWC) - Advanced Level}}
\end{itemize}

\vspace{3pt}

\noindent \normalsize \textbf{The Linux Foundation} \\
\textit{Hyperledger Mentorship Program 2021 - Mentee} \hfill 06/2021 - 12/2021
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item {\normalsize \href{https://wiki.hyperledger.org/display/INTERN/Implement+cross+chain+contract+invocation+using+ServiceMesh+way}{Hyperledger - Implement cross chain contract invocation using ServiceMesh way}
        \begin{itemize}
            \item Implemented cross-chain contract interoperability between Hyperledger Fabric and Hyperledger Besu in the 'ServiceMesh' way.
            \item Developed cross-chain smart contract on Solidity with a 2-phase Locking mechanism.
            \item Engineered sidecar relay to felicitate the contract invocation in Java spring framework.
            \item Shaped the sidecar relay to listen for solidity events and orchestrated it to trigger transactions on the other relays using REST APIs.
        \end{itemize}
    }
\end{itemize}

\noindent \normalsize \textbf{Zenithec Techware} \hfill Raipur, India \\
\textit{iOS Developer} \hfill 04/2019 - 02/2021
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item {\normalsize \href{https://apple.co/3kAiLJ0}{PetBro Business iOS Application}
        \begin{itemize}
            \item Made the complete PetBro Business iOS Application on MVVM Architecture with RxSwift support.
            \item Used RxMoya as a Network Abstraction Layer and RxNuxe for image caching and displaying.
            \item Published a library to overcome the issue of not hiding the keyboard when clicking on UIViewController.
        \end{itemize}
    }
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%RESEARCH-WORKS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \large \textbf{\textcolor{NavyBlue}{Publications \& Research Works}} \vspace{3pt} \\
\noindent \normalsize \textbf{Cross-Chain Contract Invocation with Hyperledger Firefly} \hfill 01/2023 - In Publication \\
\textit{In Collaboration with Nikos Kapsoulis (Ph.D. candidate at National Technical University of Athens)} \hfill
\begin{itemize}
    \item Proposed a cross-chain invocation methodology with Hyperledger Firefly supernode.
\end{itemize}
\noindent \normalsize \href{https://link.springer.com/content/pdf/10.1007/978-3-030-82469-3_30}{\textbf{Blockchain-Based Digital Evidence Management System } \hfill 07/2020 - 12/2020} \\
\textit{Guide: Dr. Preeti Chandrakar (Assistant Professor) at NIT Raipur} \hfill
\begin{itemize}
    \item Proposed a digital evidence management system for legal cases to store digital evidence in Hyperledger Sawtooth using IPFS in PBFT consensus mechanism.
\end{itemize}

\noindent \normalsize \href{https://dx.doi.org/10.1504/ijiids.2022.10044370}{\textbf{Echo Based Real-time Attendance System} \hfill 08/2020 - 12/2020} \\
\textit{Guide: Dr. Jairam Naik (Assistant Professor) at NIT Raipur}
\begin{itemize}
    \item  Made an Echo-based attendance system with React GUI using Quiet Modem Project to take attendance of all the available listeners in one shot.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%EDUCATIONS-CERTIFICATIONS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \large \textbf{\textcolor{NavyBlue}{Education \& Certifications}} \vspace{3pt} \\
\normalsize \textbf{Masters of Science, Trinity College Dublin} \hfill Dublin, Ireland\\
Computer Science - Future Networked Systems \hfill 09/2022 - 08/2023
\vspace{3pt}

\noindent \normalsize \textbf{Bachelor of Technology, NIT Raipur} \hfill Raipur, India \\
Computer Science and Engineering \hfill 08/2017 - 05/2021
\vspace{3pt}

\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item { \normalsize \href{https://www.credential.net/623b189c-719c-4845-b489-1b1618d4da79}{\textbf{Associate Android Developer} - Google Developers } }
    \item { \normalsize \href{https://www.coursera.org/account/accomplishments/certificate/X4CNCJXC335V}{\textbf{Classical Cryptosystems and Core Concepts} - Coursera} }
\end{itemize}
\vspace{3pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%PROJECTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \large \textbf{\textcolor{NavyBlue}{Key Projects}} \vspace{3pt}

\noindent \normalsize \textbf{Dublin Attractions} \\
\noindent \normalsize A Web application to find nearby attractions like artworks and museums from the current location in Dublin city.
\begin{itemize}
    \item Contributed to the creation of knowledge graphs using ODFs and Ontologies using OpenAPIs and GraphDB. 
    \item Established front-end WEB GUI using React and Nextjs frameworks.
\end{itemize}
\vspace{3pt}

\noindent \normalsize \href{https://github.com/kdpisda/scientific-journal-blockchain}{\textbf{Open Journal}} \\
\noindent \normalsize A decentralized platform for researchers to publish their work with fellow researchers and also review the works of other researchers to ensure trust and transparency between all the researchers.
\begin{itemize}
    \item Shaped Solidity-based smart contracts for Ethereum Blockchain Network.
    \item Illustrated the front-end Web Interface using the Angular framework.
\end{itemize}
\vspace{3pt}

\noindent \normalsize \href{https://gist.github.com/0a9d7b1a040249d1b525ab94198a42ac}{\textbf{Lua Parser + Interpreter}} \\
\noindent \normalsize A Lua Parser + Interpreter using LPegLabel with an error recovery mechanism.
\begin{itemize}
    \item Designed a simple compiler based on a specific grammar definition in Lua Programming language with the help of LPegLabel.
\end{itemize}
\vspace{3pt}

\noindent \normalsize \href{https://bit.ly/3a62RB4}{\textbf{HideKeyboardWhenTappedAround(iOS)}} \\
\noindent \normalsize A Library for hiding the keyboard when the user taps anywhere on the screen on an iPhone.
\begin{itemize}
    \item Published an iOS Swift-based library for hiding the keyboard when the user taps anywhere in the UIViewcontroller.
\end{itemize}
\vspace{3pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%TECHNICAL-SKILLS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \large \textbf{\textcolor{NavyBlue}{Technical Skills}} \vspace{3pt} \\
\noindent \normalsize \textbf{Programming Languages:} \\
\noindent \normalsize Proficient in Java, Javascript/Typescript, Python \\
\noindent \normalsize Familiar with C/C++, Swift, Kotlin, C\#, SQL, Bash, Golang, Solidity, Ruby, Lua, Rust.
\vspace{3pt}

\noindent \normalsize \textbf{Web Technologies:} \\
\noindent \normalsize HTML/CSS/SCSS, Nodejs(MERN \& MEAN Stack), Django/Flask, REST/Graphql/gRPC/Web Sockets/MQTT, React(Redux/Mobx/Recoil.js) /Angular (NgRx)/ Vue.js
\vspace{3pt}

\noindent \normalsize \textbf{Mobile Technologies:} \\
\noindent \normalsize Native iOS(Swift)/Android(Java/Kotlin), React-Native(Cross-Platform), Flutter(Cross-Platform)
\vspace{3pt}

\noindent \normalsize \textbf{Databases and Message Queue Technologies:} \\
\noindent \normalsize MySQL, Postgres, MongoDB, Cassandra, Redis, InfluxDB, Prometheus, GraphDB, Apache Kafka, RabbitMQ
\vspace{3pt}

\noindent \normalsize \textbf{DevOps:} \\
\textbf{Version Control:} Git, Perforce;\\
\textbf{Docker:} Docker with docker-compose, Docker Swarm;\\
\textbf{Kubernetes:} Kubernetes Pods, Deployments, Service, Jobs \& Cronjobs, Service Monitors, Ingress Controllers, Load balancers, SSL certificate, Cluster Issures, API Gateways(Traefik); Kubectl, Kubens, Helm, Minikube;\\
\textbf{CI/CD:} GitHub Actions, Circle CircleCI, Travis;\\
\textbf{Monitoring:} Grafana (with Prometheus or InfluxDB), Honeybadger.io,  Firebase Analytics \& Crashlytics;
\vspace{3pt}

\noindent \normalsize \textbf{Cloud/Deployment Platforms:}\\
\textbf{Google Cloud Platform(GCP):} GCP Cloud Storage, GCP Kubernetes Engine, GCP OAUTH APIs, GCP Compute Engine;\\
\textbf{Firebase:} Firebase Authentication, Firebase Storage, Firebase Firestore Database, Firebase Real-Time Database; Firebase Analytics \& Crashlytics; Firebase Admob;\\
\textbf{Amazon Web Services(AWS):} Lamda functions, S3 buckets, Elastic Kubernetes Service(EKS), Elastic Container Registry (ECR), Elastic Beanstalk(EB), Amazon API Gateways;\\
\textbf{Microsoft Azure:} Azure Kubernetes Service(AKS), Azure Container Registry (ACR);\\
\textbf{Digital Ocean:} Digital Ocean Kubernetes, Digital Ocean Droplets, Digital Ocean Serverless - Functions, Digital Ocean Apps;\\
\textbf{Vercel \& Netlify:} Static site deployment, Edge CDNs;  
\vspace{3pt}

\noindent \normalsize \textbf{Blockchain Technologies, and Others:}\\
\noindent \normalsize Ethereum Solidity, Hyperledger Fabric / Sawtooth / Firefly / Burrow / Besu, Unity3D.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%TALKS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \large \textbf{\textcolor{NavyBlue}{Talks and Bootcamps}}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item { \normalsize Given a talk on "How my fish plays Pokemon?" at Kafka Submit London 2024 on March 20th, 2024}
    \item { \normalsize Given a talk on "Python in Blockchain Interoperability" at Pycon Limerick 2023 on March 25th, 2023.}
    \item { \normalsize Given a talk on "Building insurance application on Corda Blockchain using Java" at Dublin Java User Group(DubJUG) on March 22nd, 2023.}
    \item { \normalsize Given a talk on "Managing background work on Android" in I/O Extended with GDG Raipur on June 12th, 2022.  }
    \item { \normalsize Conducted Android Study Jams in NIT Raipur on course Android Kotlin Fundamentals course on date March 15th, 2021. }
    \item { \normalsize Conducted a Bootcamp at Facebook Developer Circles Raipur on Blockchain-based Decentralized Application development in Ethereum Blockchain on March 20th, 2020. }
\end{itemize}
\vspace{3pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%ACHIEVEMENTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \large \textbf{\textcolor{NavyBlue}{Achievements}}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item { \normalsize \textbf{Winner:} EasyA x Polkadot London Hackathon 2024
        \begin{itemize}
            \item \normalsize \href{https://github.com/Shritesh99/pallet-farcaster_frame}{\textbf{Pallet Farcaster Frame:}} Developed a pallet to connect Farcaster Frames with polkadot/substrate based chains.
        \end{itemize}
    }
    \item { \normalsize \textbf{Runner Up:} ETH London 2024
        \begin{itemize}
            \item \normalsize \href{https://github.com/Shritesh99/deref}{\textbf{Deref:}}  Made "DeRefer" which is a decentralized referral system that leverages royalties to onboard users and engage communities.
        \end{itemize}
    }
    \item { \normalsize \textbf{Finals:} Smart India Hackathon 2019. 
        \begin{itemize}
            \item \normalsize \href{https://github.com/Shritesh99/airport}{\textbf{Airport-Licensing DAPP:}} Developed a decentralized application for Aerodrome Licensing for Airport Authority of India(AAI) for Aerodrome Licensing using Hyperledger Fabric with React Frontend and Android Application for the on-site officer.
        \end{itemize}
    }
    \item { \normalsize \textbf{Winner:} Codeutsava 4.0 Hackathon in Blockchain track.
        \begin{itemize}
            \item \normalsize \href{https://github.com/Shritesh99/airport}{\textbf{Airport-Licensing DAPP:}} Developed a decentralized application for Aerodrome Licensing for Airport Authority of India(AAI) for Aerodrome Licensing using Hyperledger Composer with React Frontend.
        \end{itemize}
    }
    \item { \normalsize \textbf{Finals:} Smart India Hackathon 2020. 
        \begin{itemize}
            \item \normalsize \href{https://github.com/siddharthshah3030/choukidar-owasp-security-chrome-extension}{\textbf{Choukidar Chrome Extension:}} Developed a chrome extension to detect Top 10 OWASP Security vulnerabilities in a WebSite.
        \end{itemize}
    }
    \item { \normalsize \textbf{Fourth Winner:} Dot Slash Hackathon held at NIT Surat. 
        \begin{itemize}
            \item \normalsize \href{https://bit.ly/31wXfMr}{\textbf{dEmergency:}} Developed a decentralized SOS triggering service for medical emergencies.
        \end{itemize}
    }
    \item { \normalsize \textbf{Winner:} Codeutsava 3.0 Hackathon in Blockchain track.
        \begin{itemize}
            \item \normalsize \href{https://bit.ly/healthJ}{\textbf{dOrgans:}} Developed a blockchain-based dApp in which if a person needs an organ he can register on the platform and wait until a cadaver organ(organ from a person who is dead and willing to donate his organs) is available, all this data will be stored on Ethereum based smart contract so that this sensitive information is tamper-proof.
        \end{itemize}
    }
    \item { \normalsize \textbf{Winner:} Application Development contest held IIIT Raipur. 
        \begin{itemize}
            \item \normalsize \href{https://bit.ly/CG_App}{\textbf{CG Tourism App:}} Developed a React Native-based cross-platform application for Chhattisgarh Tourism Board with Django Backend.
        \end{itemize}
    }
\end{itemize}

\end{document}
