%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%IMPORTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt]{article}

\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{fontspec}
\usepackage[hidelinks]{hyperref}
\usepackage[dvipsnames]{xcolor}
\setmainfont[Ligatures=TeX]{Verdana}

% Set default itemize options for consistent bullet formatting
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*}

\begin{document}
\begin{center}
\pagenumbering{gobble}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%HEADINGS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\LARGE Shritesh Jamulkar \\[3pt]

\large \textcolor{NavyBlue}{\href{mailto:shritesh.sj@gmail.com}{shritesh.sj@gmail.com} || \href{tel:+447405656340}{+44 740 5656302} || UK Work Authorization} \\[3pt]

\normalsize \href{https://linkedin.com/in/shritesh99}{linkedin.com/in/shritesh99} || \href{https://github.com/Shritesh99}{github.com/Shritesh99} || \href{https://leetcode.com/rxshri99}{leetcode.com/rxshri99} \\
\end{center}

\vspace{10pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%WORK-EXPERIENCE%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \large \textbf{\textcolor{NavyBlue}{Work Experience}} \\[5pt]
\noindent \normalsize \textbf{THG - The Hut Group} \hfill Manchester, UK \\
\textit{Software Engineer} \hfill Nov'23 - Present
\begin{itemize}
    \item \textbf{Stockmanager and various other microservices - In Stock and Availability Team}
    \begin{itemize}
        \item Developed scalable front-end and back-end solutions using Spring and Angular, achieving 90\%+ unit test coverage.
        \item Migrated legacy Tomcat-based services to Kubernetes and Docker, reducing deployment time by 66\%.
        \item Optimized database performance by migrating legacy queries to batched queries, cutting query wait times by 40\% and reducing application crashes.
        \item Led three key client integrations for warehouse management, resolving stock discrepancies and ensuring seamless collaboration across teams.
        \item Implemented Zabbix-based monitoring and alerting systems, boosting infrastructure uptime by 20\%.
    \end{itemize}
\end{itemize}

\vspace{5pt}

\noindent \normalsize \textbf{Samsung Research \& Development Institute, Bangalore} \hfill Bangalore, India \\
\textit{Software Engineer} \hfill Jul'21 - Oct'23
\begin{itemize}
    \item \textbf{LTE System Manager (LSM) Project - In Management Software \& Analytics Team}
    \begin{itemize}
        \item Worked on a full-stack Java Spring telecom tool (LSM) for network management, delivered on time and under budget using agile methodologies.
        \item Optimized microservice communication with RMI (Remote Method Invocation), cutting latency by 25\% and enhancing real-time network monitoring responsiveness.
        \item Designed custom error logging and exception handling, reducing debugging time for field engineers.
        \item Automated end-to-end testing for the Element Management System (EMS) using Python and Selenium, slashing manual testing efforts by 50\% and accelerating release cycles.
        \item Provided TAC3 support for 4G networks (e.g., JIO, SKT), ensuring efficient operations and issue resolution.
    \end{itemize}
    \item \textbf{Samsung Software Competency Test (SWC) - Advanced Level}
\end{itemize}

\vspace{10pt}

\noindent \normalsize \textbf{The Linux Foundation} \\
\textit{Hyperledger Mentorship Program 2021 - Mentee} \hfill Jun'21 - Dec'21
\begin{itemize}
    \item \textbf{\href{https://wiki.hyperledger.org/display/INTERN/Implement+cross+chain+contract+invocation+using+ServiceMesh+way}{Hyperledger - Implement cross chain contract invocation using ServiceMesh way}}
    \begin{itemize}
        \item Implemented cross-chain contract interoperability between Hyperledger Fabric and Besu using a ServiceMesh approach.
        \item Developed a Solidity smart contract with a 2-phase locking mechanism for secure cross-chain transactions.
    \end{itemize}
\end{itemize}

\vspace{10pt}

\noindent \normalsize \textbf{Zenithec Techware} \hfill Raipur, India \\
\textit{iOS Developer} \hfill 04/2019 - 02/2021
\begin{itemize}
    \item \textbf{\href{https://apple.co/3kAiLJ0}{PetBro Business iOS Application}}
    \begin{itemize}
        \item Developed the PetBro Business iOS app using MVVM and RxSwift, integrating RxMoya for network abstraction.
        \item Published an open-source library to resolve keyboard dismissal issues in UIViewController.
    \end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%PUBLICATIONS & RESEARCH%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{10pt}
\noindent \large \textbf{\textcolor{NavyBlue}{Publications \& Research Works}} \\[5pt]
\noindent \normalsize \textbf{Cross-Chain Contract Invocation with Hyperledger Firefly} \hfill 01/2023 - In Publication \\
\textit{In Collaboration with Nikos Kapsoulis (Ph.D. candidate at National Technical University of Athens)}
\begin{itemize}
    \item Proposed a cross-chain invocation methodology with Hyperledger Firefly supernode.
\end{itemize}

\vspace{5pt}
\noindent \normalsize \textbf{\href{https://link.springer.com/content/pdf/10.1007/978-3-030-82469-3_30}{Blockchain-Based Digital Evidence Management System}} \hfill 07/2020 - 12/2020 \\
\textit{Guide: Dr. Preeti Chandrakar (Assistant Professor) at NIT Raipur)}
\begin{itemize}
    \item Proposed a digital evidence management system for legal cases to store digital evidence in Hyperledger Sawtooth using IPFS in PBFT consensus mechanism.
\end{itemize}

\vspace{5pt}
\noindent \normalsize \textbf{\href{https://dx.doi.org/10.1504/ijiids.2022.10044370}{Echo Based Real-time Attendance System}} \hfill 08/2020 - 12/2020 \\
\textit{Guide: Dr. Jairam Naik (Assistant Professor) at NIT Raipur)}
\begin{itemize}
    \item Developed an Echo-based attendance system with a React GUI using the Quiet Modem Project to capture attendance from all available listeners in one shot.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%EDUCATION & CERTIFICATIONS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{10pt}
\noindent \large \textbf{\textcolor{NavyBlue}{Education \& Certifications}} \\[5pt]
\normalsize \textbf{Masters of Science, Trinity College Dublin} \hfill Dublin, Ireland\\
Computer Science - Future Networked Systems \hfill 09/2022 - 08/2023

\vspace{5pt}
\noindent \normalsize \textbf{Bachelor of Technology, NIT Raipur} \hfill Raipur, India\\
Computer Science and Engineering \hfill 08/2017 - 05/2021

\vspace{5pt}
\begin{itemize}
    \item \normalsize \href{https://www.credential.net/623b189c-719c-4845-b489-1b1618d4da79}{\textbf{Associate Android Developer} - Google Developers}
    \item \normalsize \href{https://www.coursera.org/account/accomplishments/certificate/X4CNCJXC335V}{\textbf{Classical Cryptosystems and Core Concepts} - Coursera}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%KEY PROJECTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{10pt}
\noindent \large \textbf{\textcolor{NavyBlue}{Key Projects}} \\[5pt]
\noindent \normalsize \href{https://github.com/Shritesh99/polkadot-nft-app-farcaster-frames}{\textbf{Farcaster Frames Polkadot Pallet}} \\
\normalsize A NFT minting application for Farcaster Frames on Polkadot - \textbf{Funded by Web3 Foundation}

\vspace{5pt}
\noindent \normalsize \href{https://github.com/Shritesh99/ppsc-build}{\textbf{Protocol Buffers Parity SCALE Codec Generator}} \\
\normalsize A Rust library to generate Parity SCALE Codec-compliant Rust code from .proto files for no\_std environment, simplifying build-time code generation for Cargo projects.

\vspace{5pt}
\noindent \normalsize \href{https://gist.github.com/0a9d7b1a040249d1b525ab94198a42ac}{\textbf{Lua Parser + Interpreter}} \\
\normalsize A Lua Parser + Interpreter using LPegLabel with an error recovery mechanism.

\vspace{5pt}
\noindent \normalsize \href{https://bit.ly/3a62RB4}{\textbf{HideKeyboardWhenTappedAround (iOS)}} \\
\normalsize A library for hiding the keyboard when the user taps anywhere on the screen on an iPhone.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%TECHNICAL SKILLS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{10pt}
\noindent \large \textbf{\textcolor{NavyBlue}{Technical Skills}} \\[5pt]
\noindent \normalsize \textbf{Programming Languages:} Java, Kotlin, Javascript/Typescript, Python, C/C++, Swift, SQL, Bash, Golang, Solidity, Rust.

\vspace{5pt}
\noindent \normalsize \textbf{Web Technologies:} Nodejs (MERN \& MEAN Stack), Django/Flask, REST/Graphql/gRPC/Web Sockets/MQTT, React, Angular

\vspace{5pt}
\noindent \normalsize \textbf{Databases and Message Queues:} MySQL, Postgres, MongoDB, Redis, Prometheus, GraphDB, Apache Kafka, ActiveMQ

\vspace{5pt}
\noindent \normalsize \textbf{DevOps:} Git, Jenkins, Kubernetes, Docker, Grafana, Prometheus

\vspace{5pt}
\noindent \normalsize \textbf{Blockchain Technologies, and Others:} Ethereum Solidity, Hyperledger Fabric/Sawtooth/Firefly/Burrow/Besu, Polkadot.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%ACHIEVEMENTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{10pt}
\noindent \large \textbf{\textcolor{NavyBlue}{Hackathons, Achievements, Talks and Bootcamps}} \\[5pt]
\begin{itemize}
    \item \normalsize \textbf{Winner:} EasyA x Polkadot London Hackathon 2024 - Built a pallet for Farcaster Frames integration.
    \item \normalsize \textbf{Runner Up:} ETH London 2024 - Created "DeRefer," a decentralized referral system using royalties.
    \item \normalsize \textbf{Finalist:} Smart India Hackathon 2019 \& 2020 (Blockchain-based DApps for AAI \& Security)
    \item \normalsize \textbf{Speaker at Conferences, Meetups:} Kafka Summit 2024, PyCon Limerick 2023, DubJUG, and local developer communities.
\end{itemize}

\end{document}
