%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%IMPORTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{article}

\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{fontspec}
\usepackage[hidelinks]{hyperref}
\usepackage[dvipsnames]{xcolor}
\setmainfont[Ligatures=TeX]{Verdana}

\begin{document}
\begin{center}
\pagenumbering{gobble}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%HEADINGS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\LARGE Shritesh Jamulkar \\

\vspace{3pt}

\large \textcolor{NavyBlue}{Passionate Developer} \\

\vspace{5pt}

\normalsize \href{mailto:shritesh.sj@gmail@gmail.com}{shritesh.sj@gmail.com} || \href{https://github.com/Shritesh99}{github.com/Shritesh99} || \href{https://linkedin.com/in/shritesh99}{linkedin.com/in/shritesh99} || \href{https://leetcode.com/rxshri99/}{leetcode.com/rxshri99/} \\
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%WORK-EXPERIENCE%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \large \textbf{\textcolor{NavyBlue}{Work Experience}} \vspace{5pt} \\
\noindent \normalsize \textbf{Samsung Research \& Development Institute, Banglore} \hfill Banglore, Karnataka \\
\textit{Software Engineer} \hfill 07/2021 - Present
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item {\normalsize {LTE System Manager (LSM) Project - In Management Software \& Analytics Team }
        \begin{itemize}
            \item Worked as a Full-Stack Developer in JAVA Spring-based LSM project, specifically in FM (Fault Module).
            \item Contributed to Python selenium-based automation testing for the entire Element Management System (EMS) software.
        \end{itemize}
    }
\end{itemize}

\vspace{5pt}

\noindent \normalsize \textbf{The Linux Foundation} \\
\textit{Hyperledger Mentorship Program 2021 - Mentee} \hfill 06/2021 - 12/2021
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item {\normalsize \href{https://wiki.hyperledger.org/display/INTERN/Implement+cross+chain+contract+invocation+using+ServiceMesh+way}{Hyperledger - Implement cross chain contract invocation using ServiceMesh way}
        \begin{itemize}
            \item Implemented cross-chain contract interoperability between Hyperledger Fabric and Hyperledger Besu in the 'ServiceMesh' way.
            \item Developed cross-chain smart contract on Solidity with a 2-Phase Locking mechanism.
            \item Developed sidecar relay to felicitate the contract invocation in Java spring framework.
        \end{itemize}
    }
\end{itemize}

\noindent \normalsize \textbf{Zenithec Techware} \hfill Raipur, Chhattisgarh \\
\textit{iOS Developer} \hfill 04/2019 - 02/2021
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item {\normalsize \href{https://apple.co/3kAiLJ0}{PetBro Business iOS Application}
        \begin{itemize}
            \item Made the complete PetBro Business iOS Application on MVVM Architecture with RxSwift support.
            \item Used RxMoya as a Network Abstraction Layer and RxNuxe for image caching and displaying.
        \end{itemize}
    }
\end{itemize}

\noindent \normalsize \href{https://bit.ly/allsoft_certificate}{\textbf{Allsoft.co}} \hfill Raipur, Chhattisgarh \\
\noindent \normalsize \textit{\href{https://bit.ly/allsoft_certificate}{Software Developer Intern}} \hfill 07/2019 - 09/2019
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item {\normalsize \href{https://bit.ly/allsoft_certificate}{GFI Auction}
        \begin{itemize}
            \item Worked on GFI Auction project based on Angular Frontend framework.
            \item Integrated NgRx Store to provide reactive state management.
        \end{itemize}
    }
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%RESEARCH-WORKS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \large \textbf{\textcolor{NavyBlue}{Research Works}} \vspace{5pt} \\
\noindent \normalsize \textbf{Cross-Chain Contract Invocation with Hyperledger Firefly} \hfill 01/2023 - Present \\
\textit{In Collaboration with Nikos Kapsoulis (PhD. Candidate at National Technical University of Athens)} \hfill
\begin{itemize}
    \item Proposed a cross-chain invocation methodology with Hyperledger Firefly supernode.
\end{itemize}
\noindent \normalsize \href{https://link.springer.com/content/pdf/10.1007/978-3-030-82469-3_30}{\textbf{Blockchain-Based Digital Evidence Management System } \hfill 07/2020 - 12/2020} \\
\textit{Guide: Dr. Preeti Chandrakar (Assistant Professor) at NIT Raipur} \hfill
\begin{itemize}
    \item Proposed a digital evidence management system for legal cases to store digital evidence in Hyperledger Sawtooth using IPFS in PBFT consensus mechanism.
\end{itemize}

\noindent \normalsize \href{https://dx.doi.org/10.1504/ijiids.2022.10044370}{\textbf{Echo Based Real-time Attendance System} \hfill 08/2020 - 12/2020} \\
\textit{Guide: Dr. Jairam Naik (Assistant Professor) at NIT Raipur}
\begin{itemize}
    \item  Made an Echo-based attendance system using Quiet Modem Project to take attendance of all the available listeners in one shot.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%EDUCATIONS-CERTIFICATIONS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \large \textbf{\textcolor{NavyBlue}{Education \& Cerifications}} \vspace{5pt} \\
\normalsize \textbf{Masters of Science, Trinity College Dublin \hfill 09/2022 - Present}\\
Computer Science - Future Networked Systems
\vspace{5pt}

\noindent \normalsize \textbf{Bachelor of Technology, NIT Raipur \hfill 08/2017 - 05/2021}\\
Computer Science and Engineering \\
Cumulative Performance Index: 7.68/10 \\
Final Semester's Performance Index: 9.27/10
\vspace{5pt}

\noindent \normalsize \textbf{Sri Shankra Vidyalaya(HSC) \hfill 04/2015 - 04/2017}\\
Intermediate \textbackslash+2 \\
Percentage: 80\% \\

\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item { \normalsize \href{https://www.credential.net/623b189c-719c-4845-b489-1b1618d4da79}{\textbf{Associate Android Developer} - Google Developers } }
    \item { \normalsize \href{https://www.coursera.org/account/accomplishments/certificate/X4CNCJXC335V}{\textbf{Classical Cryptosystems and Core Concepts} - Coursera} }
\end{itemize}
\vspace{5pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%PROJECTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \large \textbf{\textcolor{NavyBlue}{Key Projects}} \vspace{5pt}

\noindent \normalsize \textbf{Dublin Attractions} \\
\noindent \normalsize A Web application to find nearby attractions like artworks and museums from the current location in Dublin city.
\begin{itemize}
    \item Contributed to the creation of knowledge graphs using ODFs and Ontologies using OpenAPIs and GraphDB. 
    \item Developed front-end WEB GUI using the React framework.
\end{itemize}
\vspace{5pt}

\noindent \normalsize \href{https://github.com/kdpisda/scientific-journal-blockchain}{\textbf{Open Journal}} \\
\noindent \normalsize A decentralized platform for researchers to publish their work with fellow researchers and also review the works of other researchers to ensure trust and transparency between all the researchers.
\begin{itemize}
    \item Developed Solidity-based smart contracts for Ethereum Blockchain Network.
    \item Developed front-end Web Interface using the Angular framework.
\end{itemize}
\vspace{5pt}

\noindent \normalsize \href{https://gist.github.com/0a9d7b1a040249d1b525ab94198a42ac}{\textbf{Lua Parser + Interpreter}} \\
\noindent \normalsize A Lua Parser + Interpreter using LPegLabel with an error recovery mechanism.
\begin{itemize}
    \item Designed a simple compiler based on a specific grammar definition in Lua Programming language with the help of LPegLabel.
\end{itemize}
\vspace{5pt}

\noindent \normalsize \href{https://bit.ly/3a62RB4}{\textbf{HideKeyboardWhenTappedAround(iOS)}} \\
\noindent \normalsize A Library for hiding the keyboard when the user tapped anywhere on the screen on iPhone.
\begin{itemize}
    \item Published an iOS Swift-based library for hiding the keyboard when the user tapped anywhere in the UIViewcontroller.
\end{itemize}
\vspace{5pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%TECHNICAL-SKILLS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \large \textbf{\textcolor{NavyBlue}{Technical Skills}} \vspace{5pt} \\
\noindent \normalsize \textbf{Programming Languages:} \\
\noindent \normalsize Proficient in Java, Javascript/Typescript, Python \\
\noindent \normalsize Familiar with C/C++, Swift, Kotlin, C\#, SQL, Bash, Golang, Solidity, Ruby, Lua, Rust.
\vspace{5pt}

\noindent \normalsize \textbf{Web Technologies:} \\
\noindent \normalsize HTML/CSS/SCSS, Nodejs(MERN \& MEAN Stack), Django/Flask, REST/Graphql/gRPC/Web Sockets/MQTT, React(Redux/Mobx/Recoil.js) /Angular (NgRx)/ Vue.js
\vspace{5pt}

\noindent \normalsize \textbf{Databases and Message Queue Technologies:} \\
\noindent \normalsize MySQL, Postgres, MongoDB, Cassandra, Redis, InfluxDB, Prometheus, GraphDB, Apache Kafka, RabbitMQ
\vspace{5pt}

\noindent \normalsize \textbf{Mobile Technologies:} \\
\noindent \normalsize Native iOS(Swift)/Android(Java/Kotlin), React-Native(Cross-Platform), Flutter(Cross-Platform)
\vspace{5pt}

\noindent \normalsize \textbf{Deployment \& CI/CD Monitoring Technologies:} \\
\textbf{Docker:} Docker with docker-compose and CMD;\\
\textbf{Kubernetes:} Kubernetes Pods, Deployments, Service, Jobs \& Cronjobs, Service Monitors, Ingress Controllers, Load balancers, SSL certificate, Cluster Issures, API Gateways(Traefik); Kubectl, Kubens, Helm, Minikube;\\
\textbf{CI/CD:} Gihub Actions, Circle CircleCI, Travis;\\
\textbf{Monitoring:} Grafana (with Prometheus or InfluxDB), Honeybadger.io,  Firebase Analytics \& Crashlytics;
\vspace{5pt}

\noindent \normalsize \textbf{Cloud/Deployment Platforms:}\\
\textbf{Google Cloud Platform(GCP):} GCP Cloud Storage, GCP Kubernetes Engine, GCP OAUTH APIs, GCP Compute Engine;\\
\textbf{Firebase:} Firebase Authentication, Firebase Storage, Firebase Firestore Database, Firebase Real-Time Database; Firebase Analytics \& Crashlytics; Firebase Admob;\\
\textbf{Amazon Web Services(AWS):} Lamda functions, S3 buckets, Elastic Kubernetes Service(EKS), Elastic Container Registry (ECR), Elastic Beanstalk(EB), Amazon API Gateways;\\
\textbf{Microsoft Azure:} Azure Kubernetes Service(AKS), Azure Container Registry (ACR) ;\\
\textbf{Digital Ocean:} Digital Ocean Kubernetes, Digital Ocean Droplets, Digital Ocean Serverless - Functions, Digital Ocean Apps;\\
\textbf{Vercel \& Netlify:} Static site deployment, Edge CDN networks;\\  

\noindent \normalsize \textbf{Blockchain Technologies, and Others:}\\
\noindent \normalsize Ethereum Solidity, Hyperledger Fabric / Sawtooth / Firefly / Burrow, Git, Unity3D.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%RESPONSIBILITY%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{10pt}
\noindent \large \textbf{\textcolor{NavyBlue}{Position of Responsibility}} \vspace{5pt} \\
\noindent \normalsize \textbf{Technocracy - Technical Committee of NIT Raipur} \hfill Raipur, Chhattisgarh \\
\noindent \normalsize \textit{Tech Lead} \hfill 01/19 - 04/21
\begin{itemize}[noitemsep, nolistsep,leftmargin=*]
    \item {\href{https://bit.ly/aavartan}{Aavartan Android Application}
        \begin{itemize}
            \item Developed NIT Raipur's Tech Fest's mobile Aavartan application using Native Android Development which has features like Live event tracking and connecting with new people and much more.
        \end{itemize}
    }
    \item {\href{https://bit.ly/kleos2k18}{Kleos2k18 Android Application}
        \begin{itemize}
            \item Developed a Live Quiz application for NIT Raipur's Flagship Triva Event using Django framework and Native JAVA mobile application.
        \end{itemize}
    }
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%TALKS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \large \textbf{\textcolor{NavyBlue}{Talks and Bootcamps}}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item { \normalsize Given a talk on "Python in Blockchain Interoperability" at Pycon Limerick 2023 on March 25th, 2023.}
    \item { \normalsize Given a talk on "Building insurance application on Corda Blockchain using Java" at Dublin Java User Group(DubJUG) on March 22nd, 2023.}
    \item { \normalsize Given a talk on "Unlocking the power of Knowledge Graphs" in Devfest Raipur in Machine Learning Track with GDG Raipur on December 16th, 2022.  }
    \item { \normalsize Given a talk on "What is an API?" in I/O Extended - Web Edition with GDG Raipur on July 10th, 2022.  }
    \item { \normalsize Given a talk on "Managing background work on Android" in I/O Extended with GDG Raipur on June 12th, 2022.  }
    \item { \normalsize Conducted Android Study Jams in NIT Raipur on course Android Kotlin Fundamentals course on date March 15th, 2021. }
    \item { \normalsize Conducted a Bootcamp at Facebook Developer Circles Raipur on Blockchain-based Decentralized Application development in Ethereum Blockchain on March 20th, 2020. }
\end{itemize}
\vspace{10pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%ACHIEVEMENTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \large \textbf{\textcolor{NavyBlue}{Achievemnts}}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item { \normalsize \textbf{Finals:} Smart India Hackathon 2019. 
        \begin{itemize}
            \item \normalsize \href{https://github.com/Shritesh99/airport}{\textbf{Airport-Licensing DAPP:}} Developed a decentralized application for Aerodrome Licensing for Airport Authority of India(AAI) for Aerodrome Licensing using Hyperledger Fabric with React Frontend and Android Application for the on-site officer.
        \end{itemize}
    }
    \item { \normalsize \textbf{Winner:} Codeutsava 4.0 Hackathon in Blockchain track.
        \begin{itemize}
            \item \normalsize \href{https://github.com/Shritesh99/airport}{\textbf{Airport-Licensing DAPP:}} Developed a decentralized application for Aerodrome Licensing for Airport Authority of India(AAI) for Aerodrome Licensing using Hyperledger Composer with React Frontend.
        \end{itemize}
    }
    \item { \normalsize \textbf{Finals:} Smart India Hackathon 2020. 
        \begin{itemize}
            \item \normalsize \href{https://github.com/siddharthshah3030/choukidar-owasp-security-chrome-extension}{\textbf{Choukidar Chrome Extension:}} Developed a chrome extension to detect Top 10 OWASP Security vulnerabilities in a WebSite.
        \end{itemize}
    }
    \item { \normalsize \textbf{Fourth Winner:} Dot Slash Hackathon held at NIT Surat. 
        \begin{itemize}
            \item \normalsize \href{https://bit.ly/31wXfMr}{\textbf{dEmergency:}} Developed a decentralized SOS triggering service for medical emergencies.
        \end{itemize}
    }
    \item { \normalsize \textbf{Winner:} Codeutsava 3.0 Hackathon in Blockchain track.
        \begin{itemize}
            \item \normalsize \href{https://bit.ly/healthJ}{\textbf{dOrgans:}} Developed a blockchain-based dApp in which if a person needs an organ he can register on the platform and wait until a cadaver organ(organ from a person who is dead and willing to donate his organs) is available, all this data will be stored on Ethereum based smart contract so that this sensitive information is tamper-proof.
        \end{itemize}
    }
    \item { \normalsize \textbf{Winner:} Application Development contest held IIIT Raipur. 
        \begin{itemize}
            \item \normalsize \href{https://bit.ly/CG_App}{\textbf{CG Tourism App:}} Developed a React Native-based cross-platform application for Chhattisgarh Tourism Board with Django Backend.
        \end{itemize}
    }
\end{itemize}

\end{document}
