%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%IMPORTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{article}

\usepackage[top=0.2in, bottom=0.2in, left=0.2in, right=0.2in]{geometry}
\usepackage{enumitem}
\usepackage{fontspec}
\usepackage[hidelinks]{hyperref}
\usepackage[dvipsnames]{xcolor}
\setmainfont[Ligatures=TeX]{Verdana}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%HEADINGS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}

\LARGE Shritesh Jamulkar

\large \textcolor{NavyBlue}{\href{mailto:shritesh.sj@gmail@gmail.com}{shritesh.sj@gmail.com} || \href{tel:+447405656340}{+44 740 5656302} || Skilled Worker Visa} \\

\vspace{2pt}

\normalsize \href{https://linkedin.com/in/shritesh99}{linkedin.com/in/shritesh99} || \href{https://github.com/Shritesh99}{github.com/Shritesh99} || \href{https://leetcode.com/rxshri99}{leetcode.com/rxshri99} 
\end{center}

\vspace{-5pt}

\noindent \rule{\textwidth}{1pt}

\noindent \textbf{Professional Summary:} Software Engineer with 4 years of enterprise backend and full-stack expertise across Java, Python, Spring Boot, microservices, Kubernetes, and DevOps, complemented by hands-on blockchain development (Polkadot, Ethereum, Hyperledger) and a passion for protocol engineering.

\vspace{-5pt}

\noindent \rule{\textwidth}{1pt}

\vspace{5pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%WORK-EXPERIENCE%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \large \textbf{\textcolor{NavyBlue}{Work Experience}} \vspace{3pt} \\
\noindent \normalsize \textbf{THG Ingenuity} \hfill Manchester, UK \\
\textit{Software Engineer} \hfill Nov'23 - Nov'25
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item {\normalsize {Stockmanager and various other microservices - In Stock and Availability Team }
        \begin{itemize}
            \item Architected scalable microservices including Stockmanager, Dropshipmanager, Allocation service and Stock UI with \textbf{Spring and Angular frameworks} to deliver front-end and back-end e-commerce solutions, with over 90\% unit test coverage.
            \item Moved legacy \textbf{Tomcat-based servers to a Kubernetes-based architecture} and designed \textbf{Jenkins pipelines} for a seamless deployment process, reducing manual jar deployments. This improved deployment time from 30 minutes to 10 minutes using Docker-based containerized deployment.
            \item Engineered multi-database layer spanning \textbf{Microsoft SQL Server, CockroachDB, and CouchDB (SQL \& NoSQL)} reducing database overhead by 40\% through optimized batched queries."
            \item \textbf{Led 3+ key client integrations} (Warehouse, Fulfillment, Stock, Orders) processing 500K+ SKU updates daily, reducing stock discrepancies by 85\%. Provided solutions for \textbf{plug and play architecture in e-commerce domain}, and owned production support for critical integrations and incidents, while ensuring on-time delivery and smooth collaboration across various teams.
        \end{itemize}
    }
\end{itemize}

\noindent \normalsize \textbf{Samsung Research \& Development Institute, Bangalore} \hfill Bangalore, India  \\
\textit{Software Engineer} \hfill Jul'21 - Oct'23
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item {\normalsize {LTE System Manager (LSM) Project - In Management Software \& Analytics Team }
        \begin{itemize}
            \item Engineered full-stack \textbf{Java spring-based LSMR project, specializing in FM (Fault Module)} supporting 10+ telecom operators across 4 countries, managing 100K+ network events and 1000+ distinct GSM tower alarms as the core Fault Detection module.
            \item Optimized inter-service communication reducing latency by 25\% and improving network monitoring responsiveness for real-time fault detection.
            \item Designed the \textbf{Python selenium-based automation testing} for entire Element Management System (EMS) software.
        \end{itemize}
    }
    \item {\normalsize {Samsung Software Competency Test (SWC) - Advanced Level}}
\end{itemize}

\noindent \normalsize \textbf{The Linux Foundation} \\
\textit{Hyperledger Mentorship Program 2021 - Mentee} \hfill Jul'21 - Dec'21
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item {\normalsize \href{https://wiki.hyperledger.org/display/INTERN/Implement+cross+chain+contract+invocation+using+ServiceMesh+way}{Hyperledger - Implement cross chain contract invocation using ServiceMesh way}
        \begin{itemize}
            \item Designed and implemented cross-chain smart contract protocol enabling secure contract invocation between \textbf{Hyperledger Fabric and Besu}.
            \item Engineered sidecar relay to facilitate the contract invocation in Java spring framework.
        \end{itemize}
    }
\end{itemize}

\vspace{-5pt}

\noindent\rule{\textwidth}{1pt}

\vspace{5pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%RESEARCH-WORKS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \large \textbf{\textcolor{NavyBlue}{Research Publications}}
\begin{itemize}
    \item \normalsize \href{https://link.springer.com/content/pdf/10.1007/978-3-030-82469-3_30}{\textbf{Jamulkar, S.}, Chandrakar, P., Ali, R., Agrawal, A. and Tiwari, K., 2021, March. Evidence management system using blockchain and distributed file system (ipfs). In International Conference on Machine Learning and Big Data Analytics (pp. 337-359). Cham: Springer International Publishing.}
    \item \normalsize \href{https://dx.doi.org/10.1504/ijiids.2022.10044370}{\textbf{Jamulkar, S.}, Verma, M.K. and Naik, K.J., 2022. An echo-based autonomous real-time system for efficient maintenance of students attendance. International Journal of Intelligent Information and Database Systems, 15(4), pp.353-376.}
\end{itemize}

\vspace{-5pt}

\noindent\rule{\textwidth}{1pt}

\vspace{5pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%EDUCATIONS-CERTIFICATIONS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \large \textbf{\textcolor{NavyBlue}{Education \& Extra Curricular Activities}} \vspace{3pt} \\
\normalsize \textbf{Masters of Science, Trinity College Dublin} \hfill Dublin, Ireland\\
Computer Science - Future Networked Systems \hfill Sep'22 - Aug'23
\vspace{3pt}

\noindent \normalsize \textbf{Bachelor of Technology, NIT Raipur} \hfill Raipur, India \\
Computer Science and Engineering \hfill Aug'17 - May'21

\vspace{5pt}

\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item { \normalsize \textbf{Conference Talks} - Kafka Summit 2024, PyCon Limerick 2023 }
    \item { \normalsize \textbf{EasyA x Polkadot London Hackathon 2024} - Built a pallet for Farcaster Frames integration. \href{https://github.com/Shritesh99/pallet-farcaster_frame}{\textcolor{NavyBlue}{\underline{Link to repository}}}}
\end{itemize}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%TECHNICAL-SKILLS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \noindent \large \textbf{\textcolor{NavyBlue}{Technical Skills}} \vspace{3pt} \\
% \noindent \normalsize \textbf{Programming Languages:} \\
% \noindent \normalsize Proficient in Java, Javascript/Typescript, Python \\
% \noindent \normalsize Familiar with C/C++, Swift, Kotlin, C\#, SQL, Bash, Golang, Solidity, Ruby, Lua, Rust.
% \vspace{3pt}

% \noindent \normalsize \textbf{Web Technologies:} \\
% \noindent \normalsize HTML/CSS/SCSS, Nodejs(MERN \& MEAN Stack), Django/Flask, REST/Graphql/gRPC/Web Sockets/MQTT, React(Redux/Mobx/Recoil.js) /Angular (NgRx)/ Vue.js / Java Spring
% \vspace{3pt}

% \noindent \normalsize \textbf{Mobile Technologies:} \\
% \noindent \normalsize Native iOS (Swift)/Android(Java/Kotlin), React-Native(Cross-Platform), Flutter(Cross-Platform)
% \vspace{3pt}

% \noindent \normalsize \textbf{Databases and Message Queue Technologies:} \\
% \noindent \normalsize MySQL, Postgres, MongoDB, Cassandra, Redis, InfluxDB, Prometheus, GraphDB, Apache Kafka, RabbitMQ
% \vspace{3pt}
\end{document}